% !Mode:: "TeX:UTF-8" %
\documentclass[onecolumn,conference]{IEEEtran}
\usepackage{mathrsfs}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{multicol}
\usepackage{comment}
\usepackage{graphics}
\usepackage{picins}
\usepackage{graphicx,subfigure}
\newtheorem{Theo}{Theorem}
\newtheorem{Lemm}{Lemma}
\usepackage{multirow} 
\usepackage[xetex,colorlinks,pagebackref,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{array}
\usepackage{stfloats}
\usepackage{tabularx}
\usepackage{float}
\usepackage[ruled]{algorithm2e}
\usepackage{siunitx}
\usepackage{setspace}
\begin{document}
%\begin{spacing}{3.0}%%?????double-space
\title{Abstract}
\author{\IEEEauthorblockN{Kezhong Zhang}\today}
\maketitle
\section{What}
\begin{enumerate}
\item Extreme learning machines (ELMs) have proven to be efficient and effective learning mechanisms for pattern classification and regression. \cite{Huang2014}
\item Extreme learning machine (ELM), which was originally proposed for “generalized” single-hidden layer feedforward neural networks (SLFNs), provides efficient unified learning solutions for the applications of feature learning, clustering, regression and classification. \cite{Huang2015} \item Machine learning and artificial intelligence have seemingly never been as critical and important to real-life applications as they are in today’s autonomous, big data era.\cite{Kasun2013}
\item Consequently, ELMs, which can be biologically inspired, offer signifi cant advantages such as fast learning speed, ease of implementation, and minimal human intervention.\cite{Kasun2013}
\item Modulation type is one of the most important characteristics used in signal waveform identification and classification. \cite{HassanFebruary2012}
\item Spatial correlation is a crucial factor for practical multiple-input multiple-output (MIMO) systems. \cite{HassanFebruary2012}
\item Modulation type is one of the most important characteristics used in signal waveform identification and classification. \cite{HassanFebruary2012}
\end{enumerate}
\section{Contrast}
\begin{enumerate}
\item However, the performance of IPSs suffers from noisy measurements. In this paper, two kinds of robust extreme learning machines (RELMs), corresponding to the close-to-mean constraint, and the smallresidual constraint, have been proposed to address the issue of noisy measurements in IPSs. \cite{Lu2016}
\item However, ELMs are primarily applied to supervised learning problems. Only a few existing research papers have used ELMs to explore unlabeled data. In this paper, we extend ELMs for both semi-supervised and unsupervised tasks based on the manifold regularization, thus greatly expanding the applicability of ELMs. \cite{Huang2014}
\item Different from the common understanding and tenet that hidden neurons of neural networks need to be iteratively adjusted during training stage, ELM theories show that hidden neurons are important but need not be iteratively tuned. \cite{Huang2015}
\item In contrast to deep networks, MLELM doesn’t require fine-tuning.\cite{Kasun2013}
\end{enumerate}
\section{History}
\begin{enumerate}
\item The recently developed local learning methods provide a remedy by partitioning the feature space into a number of clusters and learning a simple local model for each cluster. \cite{Zhang2016}
\end{enumerate}
\section{Our Work}
\begin{enumerate}
\item This paper studies the general architecture of locally connected ELM, showing that: 1) ELM theories are naturally valid for local connections, thus introducing local receptive fields to the input layer; 2) each hidden node in ELM can be a combination of several hidden nodes (a subnetwork), which is also consistent with ELM theories.\cite{Huang2015}
\item This paper
addresses the problem of blind digital modulation identification in spatially-correlated MIMO systems. \cite{HassanFebruary2012}
\item In this paper, an algorithm for blind digital modulation identification for multiple-input multiple-output (MIMO) systems is proposed. \cite{HassanFebruary2012}
\item Over the last decade Multiple-Input Multiple-Output (MIMO) systems have shown a great importance as they provide a reliable and high-data-rate wireless communications. \cite{HassanFebruary2012}
\end{enumerate}
\section{Experimental Results}
\begin{enumerate}
\item Simulations and real-world indoor localization experiments are \textbf{extensively carried out} and the results demonstrate that the proposed algorithms can not only improve the accuracy and repeatability, but also reduce the deviation and worst case error of IPSs compared with other baseline algorithms. \cite{Lu2016}
\item Experimental results demonstrate that the proposed method can use much less local models and time to achieve comparable or superior results to state-of-the-art SISR methods, providing a highly practical solution to real applications. \cite{Zhang2016}
\item Experimental results on the NORB dataset, a benchmark for object recognition, show that compared with conventional deep learning solutions, the proposed local receptive fields based ELM (ELM-LRF) reduces the error rate from $6.5\%$ to $2.7\%$ and increases the learning speed up to 200 times.\cite{Huang2015}
\end{enumerate}
\bibliographystyle{IEEEtran}
%\IEEEtriggeratref{13}
\bibliography{reference}
%\end{spacing}
\end{document}
